Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
general updates

Now there are a number of different approaches to building physical quantum computing hardware being pursued by various research groups
and companies, each with their own pros and cons. Some of the types of implemented qubits include trapped ions, nitrogen-vacancy centres,
 quantum silicon photonics and superconducting, to name but a few. The type used here is the Xmon transmon qubit, a superconducting qubit
  built around a superconducting quantum interference device, or SQUID. Variations of the superconducting qubit are being developed by
  companies such as D-wave, IBM and Rigetti in the current race for quantum supremacy.

\noindent\setlength{\fboxsep}{0.5em}
\fbox{\begin{minipage}[c]{31em}%
\centerline{\textbf{Experimental realisation (SQUID)}}
The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of
superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are
charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features,
 which include easy fabrication, fast qubit control and long qubit coherence times.

@@

As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
 and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
 error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
 where classical techniques fail in solving traditionally intractable problems.

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage Quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
  development of superconducting qubits for scalable quantum hardware".

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
 in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped offer new
 avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.

>>>>

There are a number of different approaches to building physical quantum computing hardware being pursued by various research groups and companies,
each with their own advantages and disadvantages. Some of the types of experimentally implemented qubits include trapped ions, nitrogen-vacancy centres,
 quantum silicon photonics and superconducting, to name but a few. The qubits used to implement the both phase estimation algorithm and the variational
  quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.
  A SQUID is made of a superconducting loops and Josephson junctions. The state of a qubit is determined by how many pairs of electrons tunnel
  across the Josephson junctions. Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
  current race for quantum supremacy.

\noindent\setlength{\fboxsep}{0.5em}
\fbox{\begin{minipage}[c]{31em}%
\centerline{\textbf{Experimental Implementation of Quantum Hardware}}

The physical quantum hardware used to implement the VQE and PEA algorithms are Xmon qubits. The Xmon qubit is a variation of the transmon qubit,
a class superconducting qubit which uses superconducting quantum interference devices, also known as SQUIDs. It is a type of charge qubit, which is
to say it is a qubit where it’s `0’ and `1’ basis states are charge states, and the superposition of these charge states is tuned using microwave
resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.

@@

As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the variational quantum eigensolver may have better error resilience than that of standard gate model approach represented by the
phase estimation algorithm. The expectation is that this work will pave the way for the development of further quantum techniques for calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. The VQE requires only short state preparation
 and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction. This improves the efficiency
 and robustness to error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique
  might succeed where classical techniques fail in solving traditionally intractable problems.

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a promising validation of the
  development of superconducting qubits for scalable quantum hardware". And it certainly heralds an interesting future for the use both of
  superconducting qubits and variational quantum algorithms for tackling classically intractable problems in quantum chemistry and beyond.

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
 in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped to offer new
 avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico, thereby reducing
 the need for expensive trial-and-error approaches to research and development.
